A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-05-30 paper.tex
Update thesis title
Add Abstract

\title{A Decentralized Pub/Sub System for Trusted Machine Economy}

@@

\begin{abstract}

\end{abstract}

@@

\section{Introduction}
%TODO: cite examples
In the Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.

@@

In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger technologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}. The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency. Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management. These three keys meet the requirements mentioned previously.

>>>>

\title{A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading}
% Chinese title: 針對物聯網資料交易的去中心化基礎建設

@@

\begin{abstract} 
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. For instance, smart meter data can assist in energy transition. Meanwhile, time smart meter data is privacy-sensitive, that implies power consumption can be associated with appliances used and eventually can be used to track somebody's behavior and location. Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers. Finally, we implement and elevuate the performance of the prototype.
\end{abstract}

@@

\section{Introduction}
%TODO: cite examples
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.

@@

In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}. The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency. Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management. These three keys meet the requirements mentioned previously.
